---
title: "PSY8960 Final Project: Web Application"
author: "Joy Zhou"
date: "2023-05-04"
output: html_document
---

# Script Settings and Resources
```{r, message=F}
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
library(tidyverse)
```

# Data Import and Cleaning
```{r}

## Read in the dataset saved in Part 1
ion_tbl <- read_csv("../data/ion_final_tbl.csv")

```

# Data Export
```{r}

## Select only the variables that we will need for building the shiny app and save it in RDS format in the shiny folder
ion_tbl %>%
  select(MonthlyIncome, Attrition, JobSatisfaction,
         Department, EducationField, Gender, JobRole) %>%
  saveRDS(file = "../shiny/ion_tbl.RDS")

```

# An interactive web app for this project is available by [clicking this link ](https://joyzhou.shinyapps.io/people_dashboard/).

# Rationales behind shiny app codes:

## First, I set up several selectInput in order to allow users to select outcomes and data subsets.

## Second, I set up the plot output by first filtering the complete dataset by the options selected by the users, and then generating distribution plots for the selected outcome. I created a barplot for attrition and histograms for the other two outcomes because the former is a character variable. Although I could convert it into numeric values, I thought leaving it as characters would be easier for users to understand. 

## Lastly, I set up the table output by first creating a blank list, and then fill up the list based on the specific options chosen by the user. Then I used the list to group the dataset and calculate the means and sds of the outcome selected by the user. After completing all the steps above, I tested and deployed the app. 

